\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}

\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


\name{Jonathan E. McAvoy}

\address{208 Abbey Lane, Logan Township, NJ 08085}

\address{(856) 357-2550 \\ mcavoyj5@students.rowan.edu}

\begin{document}

    \begin{rSection}{Education}

        {\bf Bachelor of Science, Electrical and Computer Engineering} \hfill {anticipated May 2020}
        \\
        Rowan University  GPA:  3.751 / 4.000, Dean's List

        \end{rSection}

%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNICAL SKILLS}

        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{0ex}} l }
                &
                %Apache $\vert$
                Bash $\vert$
                C $\vert$
                C++ $\vert$
                C\# $\vert$
                HTML $\vert$
                Java $\vert$
                JavaScript $\vert$
                MATLAB $\vert$
                %Nodejs $\vert$
                PHP $\vert$
                Python $\vert$
                %Reactjs $\vert$
                Rust $\vert$
                SQL $\vert$
                Swift $\vert$
                Verilog
                \\

%           Interests&
            &
            Software Engineering, Linux Development, and Embedded Systems

               \\

        \end{tabular}

    \end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNICAL PROJECTS}

%------------------------------------------------

\begin{rSubsection}{Autonomous Quadcopter}{September 2017 - Present}{Rowan RAS}{}
\item Fully autonomous drone capable of navigating to waypoints, dropping a
  payload, and detecting targets using image recognition.
\item Integrates a fight controller, SOC image processing, navigation sensors
  and a custom power regulation circuit, on a custom designed aluminum frame.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Lab Log Tool}{May 2018 - September 2018}{Harris Cooperation, Project Lead}{}
\item Web application used by FAA employees to record lab logs, schedule lab times, and generate metrics.
\item Back-end: Linux server running a Nodejs web server, a Postfix mail server, and MySQL database.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Augmented Reality Using Structured Light (ARSL)}{September 2018 - Present}{Junior Clinic}{}
\item A novel image processing method for creating an AR environment using
  projected light and a camera.
\item Developed MATLAB, C++, and Android proof of concept applications using the
  ARSL method.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Rowan Resource Center Server}{September 2017 - Present}{A-Team, Project Lead}{}
\item Linux server running multiple virtual machines, a web server written in Rust, and MySQL database.
\item Hosts web applications for tracking employee hours, equipment loans, 3D printer queue, and chemical inventories.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Profhacks Website}{September 2017 - Present}{Rowan IEEE, Project Lead}{}
\item Nodejs-based website for Rowan IEEE's annual Hackathon.
\end{rSubsection}

%------------------------------------------------

%\begin{rSubsection}{Rowan IEEE Website}{September 2017 - Present}{Rowan IEEE}{}
%\item Apache-based website for Rowan IEEE.
%\end{rSubsection}
%
%------------------------------------------------

%\begin{rSubsection}{8-bit Discrete Processor}{June 2017 - Present}{Rowan RAS, Project Lead}{}
%\item An 8-bit processor constructed using only discrete IC logic gates.
%\end{rSubsection}

%------------------------------------------------

%\begin{rSubsection}{Android Things Facial Recognition}{November 2017 - December 2017}{Google Hackathon}{}
%\item Android IOT device that uses Google tensor flow to perform facial recognition to differentiate between users.
%\end{rSubsection}

%------------------------------------------------

%\begin{rSubsection}{Smart Mirror}{December 2016 - February 2017}{Sophomore Clinic Project}{}
%\item Raspberry Pi IOT mirror with facial recognition that displays time, weather, and news through a two-way mirror.
%\end{rSubsection}


%------------------------------------------------

%\begin{rSubsection}{EEG Controller}{February 2017 - May 2017}{Sophomore Clinic Project}{}
%\item Smart phone app that reads brain wave data from a custom wearable EGG.
%\end{rSubsection}

\end{rSection}


%   EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{WORK EXPERIENCE / INTERNSHIPS} \itemsep -3pt
{ECE Resource Center Technologist, Rowan Apprentice Engineering Team (A-Team)} \hfill January 2018 - Present\\
{Datacom Intern, Harris Cooperation} \hfill May 2018 - September 2018\\
{Chemical Engineering Lab Assistant, Rowan University} \hfill February 2017 - September 2017\\
{Data Entry and QA Intern, Siegfried USA, LLC} \hfill June 2016 - September 2016\\
{VR Intern, Virtual Reality Center, Rowan University} \hfill May 2016 - August 2016
\end{rSection}

\begin{rSection}{Professional Societies/Awards} \itemsep -3pt
{\textbf{Rowan University IEEE Student Branch (Rowan IEEE)}, Service Chair, Student Member of the Month}\\
{\textbf{Robotics and Automation Society Student Branch (Rowan RAS)}, Project Coordinator Chair}\\
{\textbf{Engineers Without Borders Student Branch}, Web Master}\\
\end{rSection}

\end{document}
